Massively Parallel Monte Carlo Methods for Linear and Nonlinear Problems

### 2012-10-02 doc/prelim/document/chapters/research_proposal/research_proposal.tex
working on intro slide drafts

We culminate our research and development with a challenge problem by
applying these new Monte Carlo methods in the Drekar multiphysics
code. With Drekar, we look forward to providing a new and robust
solution method at the production scale. Using these tools and a
leadership class computing platform, we will provide performance
measurements for the Monte Carlo solvers and compare them to
conventional methods currently leveraged within Drekar. Given the
potential to improve computational performance in production
environments such as Drekar, these new methods have the potential to
help meet the high-fidelity modeling and simulation needs of the
nuclear community.

>>>>

We culminate our research and development with a challenge problem by
applying these new Monte Carlo methods in the Drekar multiphysics
code. With Drekar, we look forward to providing a new and robust
solution method at the production scale. Using these tools and a
leadership class computing platform, we will provide performance
measurements for the Monte Carlo solvers and compare them to
conventional methods currently leveraged within Drekar. Given the
potential to improve computational performance in production
environments such as Drekar, these new methods have the potential to
help meet the high fidelity modeling and simulation needs of the
nuclear community.

### 2012-10-02 doc/prelim/presentation/prelim_presentation.tex
working on intro slide drafts

\begin{frame}{Introduction}

%%---------------------------------------------------------------------------%%
\begin{frame}{Physics-Based Motivation}

%%---------------------------------------------------------------------------%%
\begin{frame}{Hardware-Based Motivation}

>>>>

%%---------------------------------------------------------------------------%%
\begin{frame}{Introduction}
  \begin{itemize}
    \item Predictive modeling and simulation capability yields nuclear
      system designs that are safer and better performing.
    \item Modern work focused on this task leverages multiple physics
      simulation (CASL, NEAMS).
    \item New hardware drives algorithm development (petascale and
      exascale).
    \item Monte Carlo methods have the potential to provide great
      improvements that permit finer simulations and better mapping to
      future hardware.
    \item A set of massively parallel Monte Carlo methods is proposed
      to advance multiple physics simulation on contemporary and
      future leadership class machines.
  \end{itemize}
\end{frame}

%%---------------------------------------------------------------------------%%
\begin{frame}{Physics-Based Motivation}
  \begin{itemize}
    \item Predictive nuclear reactor analysis enables tighter design
      tolerance for improved thermal performance and efficieny, higher
      fuel burn-up, and high confidence in accident scenario models.
    \item Neutronics, thermal hydraulics, computational fluid
      dynamics, and structural mechanics among other physics
      contribute to these predictive models.
    \item Couplings are complicated and consistent models yield
      nonlinearities in the variables through feedback effects.
    \item  Capturing  these   effects  requires  tremendous  resources
      with $O(\sn{1}{9})$ element meshes and $O(100,000)+$ cores used
      in today's simulations.
  \end{itemize}
\end{frame}

%%---------------------------------------------------------------------------%%
\begin{frame}{Physics-Based Motivation: DNB}
  \begin{figure}[htpb!]
    \begin{center}
      \scalebox{1}{ \input{dnb_example.pdftex_t} }
    \end{center}
    \caption{\textbf{Multiphysics dependency analysis of departure from
        nucleate boiling.} \textit{A neutronics solution is required to
        compute power generation in the fuel pins, fluid dynamics is
        required to characterize boiling and fluid temperature and
        density, heat transfer is required to compute the fuel and
        cladding temperature, and the nuclear data modified with the
        temperature and density data. Strong coupling among the
        variables creates strong nonlinearities.}}
    \label{fig:dnb_example}
  \end{figure}
\end{frame}

%%---------------------------------------------------------------------------%%
\begin{frame}{Hardware-Based Motivation}
  \begin{itemize}
    \item
  \end{itemize}
\end{frame}
